### 2021-05-11 concurrency/docs/theory/theory.tex
typo

Note that Borrow-Ghost-Refinement-Exchange allows us to utilize a borrow in the extension world $\delta \refines \gamma$ but \emph{not} a borrow in the base world $\gamma$. This is important as we would have an unsoundness otherwise. In general, we can't have any rule that allows a borrow in the $\gamma$ world to flow back to the $\delta \refines \gamma$ world, as then that borrow could ``interfere''

>>>>

Note that Borrow-Ghost-Refinement-Exchange allows us to utilize a borrow in the extension world $\delta \refines \gamma$ but \emph{not} a borrow in the base world $\gamma$. This is important as we would have an unsoundness otherwise. In general, we can't have any rule that allows a borrow in the $\gamma$ world to flow back to the $\delta \refines \gamma$ world, as then that borrow could ``interfere'' with the $\delta\refines\gamma$-world's state which is being held ``in reserve'' for that borrow.
